### 2019-03-28 manuscript.tex
Update manuscript.tex

Social norm is \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} a fundamental approach in understanding FGC practice while human rights and feminist theory entails \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} entails reasons of intervening and abolishing	the practices.  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC targeting women's social networks, which are intergenerational, interdependent and interconnected across generations and genders was proposed \cite{Mack00, DuncWand11, ShelWand11}.

There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}. Both convention theory and gender approaches centre on values of how FGC associates with identity \cte{cites}.  Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), gender perspective can shed lights on how women’s gender values intertwine with convention theory of FGC values \cite{cites}.   Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.

@@

The main response variables were woman's intention to cut their daughters in the daughter model and the daughter-future model, and woman's attitude on whether FGC should be continued in the FGC future model.  The main predictors were woman's FGC status, beliefs of FGC benefits and attitudes of gender equality.  Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs. rural) in addition to country.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

@@

@@

@@

@@

% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cfcmt{I don't know if I want to cite \cite{EffeVogt15}.  It doesn't cite some very important papers which had addressed the concerns/questions the paper suggested}).

>>>>

Social norm is \cite{DuncWand11, EffeVogt15, Hayf05, Mack96, Mack00, Youn02} a fundamental approach in understanding FGC practice while human rights and feminist theory entails \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} and modernization theory \cite{BoylMcMo02, (see BellNova15 and Hayf05 for reference)}entails reasons of intervening and abolishing the practices.  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  FGC was also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC targeting women's social networks, which are intergenerational, interdependent and interconnected across generations and genders was proposed \cite{Mack00, DuncWand11, ShelWand11}.

There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns: for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}. Both convention theory and gender approaches centre on values of how FGC associates with identity \cte{cites}.  Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), gender perspective can shed lights on how women’s gender values intertwine with convention theory of FGC values \cite{cites}.   Modernization theory proposed that, for example, education and \cite{BoylMcMo02, Youn02} can contribute to the reduction of FGC practice.  Multiple theoretical frameworks would have to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{Hayf05, EffeVogt15, ModrLiu13}.

@@

The main response variables were woman's intention to cut their daughters in the daughter model and the daughter-future model, and woman's attitude on whether FGC should be continued in the FGC future model.  The predictors were selected based on literature and three main theories which have developed to account for the practice of FGC (i.e., convention theory, feminist theory and modernization theory) \cite{Fay05, BellNova15}.  The main predictors were woman's FGC status, beliefs of FGC benefits and attitudes of gender equality.  Other socio demographic variables were also included:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, media and residence (urban vs. rural) in addition to country.  The followings were treated as random variables:  cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).

@@

% Comparison of individual vs. village contribution to the variation of women’s fgc status to fgc future (see Fig 2 https://www.sciencedirect.com/science/article/pii/S0304387815000620#bb0230)

@@

% The findig “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors. This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.” \cite{BellNova15}

@@

% suggestions:  to invite elder woman to participate in reducing FGC \cite{ShelMore18}

@@

% (Against common belief of a critical mass, an empirical model showed that FGC was not driven by a social norm based on coordination and there was no signal critical threshold for the practice because of various heterogeneity of the population \cite{EffeVogt15} \cfcmt{I don't know if I want to cite \cite{EffeVogt15}.  It doesn't cite some very important papers which had addressed the concerns/questions the paper suggested}).  Can heterogeneity explain the differences of beliefs in FGC benefits at individual level vs. at a community level?
